HealpixNet: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2018-08-10 scnn.tex
change during the call

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{color}
\usepackage{url}
\usepackage{hyperref}
% \usepackage[draft]{hyperref}
\usepackage{graphicx,array} \graphicspath{{figures/}}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{bm}
\usepackage{aasmacros}

@@

\section*{TODO list}
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
	\item (TK) Related work in cosmo. The only cosmological applications of spherical CNNs in the related work are about projection on the tangent plane \citep{schmelze2017cosmologicalmodel, fluri2018deep, gupta2018nongaussianinformation}. Aren't there applications in cosmology for the other (c.f. related work section) approaches? Most of them are illustrated in omnidirectional imagery.
	\item (MD) distinction between CNN and FCN
    \item (first version done!)(NP+MD) paragraph on our chosen architecture in the Experiments sections
    \item (Done) (NP) vertex interpretation
    \item (MD) Are you happy with the vertex interpretation in section 2.5 Efficient convolutions?
    \item (NP) Finalise readme on Github code
    \item branch with notebooks with plots (results) NP
    \item NP move the repo to HealpixNet
    \item check if papers which appear as arxiv were not published in a conference or journal
    \item TK check part sphere notebook and whole sphere
    \item (done!) (TK) update the README for data zip - file from NP
    \item (almost done) TK read everything
    \item (done!) (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook. \nati{We need to talk about that.}
    \item (done!) (TK) re-make figures to make the labels/legend/titles the same font size as the main text
    \item (done!) (TK) add info on comparison with histograms, so that it's just a demonstration
    \item (done!) (TK) add reference to figure (pooling) to the area of orders
    \item (done!) (TK) add section in conclusions/ paragraph on possible extensions to the code: dense output, regression, GANs, segmentation
	\item Beware to not confuse reader with synonyms, e.g. pixelization and sampling.
    \item Check names: HealpixNet, HealpixCNN, HealpixFCN
    \item Be sure that the convolution on SO(3) is clear: we want to say (a) is the one associated with the SO(3) rotation group (b) can be performed  in the spectral domain by a multiplication (c) is equivariant to rotation (d) is described well in Section 2 of \citep{kondor2018clebsch}.
	\item Have a "Contributions" paragraph?
	\item Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices.
	\item Try to make the paper shorter?
	\item Font: do we have to use times (set in the documentclass)? I (MD) find the rendering of math a bit ugly.
\end{itemize}

>>>>

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{color}
\usepackage{url}
% \usepackage{hyperref}
\usepackage[draft]{hyperref}
\usepackage{graphicx,array} \graphicspath{{figures/}}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{bm}
\usepackage{aasmacros}

@@

\section*{TODO list}
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item (TK) check text figure 1
	\item (TK) Related work in cosmo. The only cosmological applications of spherical CNNs in the related work are about projection on the tangent plane \citep{schmelze2017cosmologicalmodel, fluri2018deep, gupta2018nongaussianinformation}. Aren't there applications in cosmology for the other (c.f. related work section) approaches? Most of them are illustrated in omnidirectional imagery.
	\item (MD) distinction between CNN and FCN
    \item (first version done!)(NP+MD) paragraph on our chosen architecture in the Experiments sections
    \item (MD) Are you happy with the vertex interpretation in section 2.5 Efficient convolutions?
    \item (TK) check if papers which appear as arxiv were not published in a conference or journal
    \item (TK) check part sphere notebook and whole sphere
    \item (TK) read everything
    \item (NP) Put Raphael in the dataset author. 
    \item (done!) (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook. \nati{We need to talk about that.}
    \item (TK) color text in 2.8
    \item (NP) D.18 text size bigger
    \item (NP) Remove caption B.13
	\item Beware to not confuse reader with synonyms, e.g. pixelization and sampling.
    \item Check names: HealpixNet, HealpixCNN, HealpixFCN
    \item (NP) Check the wording. Be sure that the convolution on SO(3) is clear: we want to say (a) is the one associated with the SO(3) rotation group (b) can be performed  in the spectral domain by a multiplication (c) is equivariant to rotation (d) is described well in Section 2 of \citep{kondor2018clebsch}.
    \item Change equation after (2) and check all kroneker
	\item Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices.
	\item Try to make the paper shorter?
	\item (TK) Font: do we have to use times (set in the documentclass)? I (MD) find the rendering of math a bit ugly.
    \item (TK) fix the bibliography
    \item Check links in footnotes.
\end{itemize}
